Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-03-08 documents/TriangleScenarioArXiv/ts.tex
final last minute edits

    \section{Violations \& Noise}
    \label{sec:violations_noise}
    Causal compatibility inequalities for the Triangle structure (such as those derived in \cref{sec:deriving_inequalities}) offer an avenue into studying quantum non-classicality. In this section, we make use of two methods, exposure to noise and numerical optimization, to further understand the nature of quantum non-classicality in connection to compatibility inequalities.

@@

    \subsection{Parameterizing Quantum Distributions}
    \label{sec:param_quantum_dist}
    \begin{figure}
    \begin{center}
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational}}
            \caption{The Triangle structure as modeled by quantum states and measurements.}
            \label{fig:triangle_structure_quantum_model}
    \end{center}
    \end{figure}
    In search of new, incompatible, quantum distributions that can be realized on the Triangle structure, numerical optimizations over the the space of quantum-accessible probability distributions are performed. To do so, we are interested in a parameterization all distributions that can be expressed as follows:
    \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
    Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately\footnote{$\netperm$ is discussed more thoroughly in \cref{sec:perm_matrix}.}.

@@

    In order to parameterize all such distributions, we elect to parameterize the states and measurements separately. Although there are numerous techniques that can used when parameterizing quantum states and measurements~\cite{Petz_2015, Hedemann_2013,Fujii_2005,James_2001,Grasmair_2014,Neilsen_Chaung_2011}, a single technique is presented that was found to be most computationally suitable for our purposes.
    \subsection{Numerical Optimization Results}
    \label{sec:results}

    \Cref{sec:param_quantum_dist} expounded on how we elected to parameterized the space of quantum distributions that can be realized on the quantum Triangle structure (\cref{fig:triangle_structure_quantum_model}). Specifically, we make use of fully generic $4\times 4$ density matrices (bipartite qubit) for each shared resource and $4$-element projective measurements. For each inequality $I$, we define the relative violation $V_F$ to be maximum violation relative to the violation achieved by the Fritz distribution.
    \[ V_F = \f{\min_{P}\bc{I\br{P}}}{I\br{P_F}} \]

@@

    Fritz's Problem is concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}. When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a single bipartite quantum state. In the Triangle structure, the observable nodes $A,B,C$ have access to potentially three different bipartite quantum states. As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.}. The question, as proposed by \ref{r:2}, remains: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states? Finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure. Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_scenario}) into the Triangle structure via the re-imagined version of the Triangle scenario (\cref{fig:triangle_structure_with_fritz_bell_embedded}). Furthermore, the logic of \cref{sec:fritz_distribution} shows that \textit{any} Bell structure compatibility inequality can be upgraded to a compatibility inequality for the Triangle structure, provided one restricts the domain of those inequalities to distributions possessing appropriate perfect correlations. Suppose one relaxed that restriction, then it becomes qualitatively reasonable to associate incompatibility via violations of upgraded inequalities with the same variety of incompatibility that is familiar in the Bell structure. Therefore, satisfying all such upgraded inequalities is a sufficient condition for a new type of incompatibility that is genuinely distinct from Bell structure incompatibility. In summary, it remains unclear whether or not \ref{r:1} or \ref{r:2} is a harder problem or if either is even feasible.

@@

    \clearpage
    \section{Quantum Parameterization of Triangle Structure}

    \subsection{Unitary Group}
    \label{sec:unitary_group}
    To facilitate the parameterization of quantum states states and PVMs, a parameterization of the unitary group of dimension $d$ (denoted $\s{U}\br{d}$) by Spengler, Huber and Hiesmayr~\cite{Spengler_2010_Unitary} is introduced. Discussions of its application to states and measurements are deferred to \cref{sec:states} and \cref{sec:measurements} respectively.

>>>>

    \section{Noisy Distributions \& Numerical Optimizations}
    \label{sec:violations_noise}
    Causal compatibility inequalities for the Triangle structure (such as those derived in \cref{sec:deriving_inequalities}) offer an avenue into studying quantum non-classicality. In this section, we make use of two methods, exposure to noise and numerical optimization, to further understand the nature of quantum non-classicality in connection to compatibility inequalities.

@@

    % \subsection{Parameterizing Quantum Distributions}
    \begin{figure}
    \begin{center}
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational}}
            \caption{The Triangle structure as modeled by quantum states and measurements.}
            \label{fig:triangle_structure_quantum_model}
    \end{center}
    \end{figure}
    In search of new, incompatible, quantum distributions that can be realized on the Triangle structure, numerical optimizations over the the space of quantum-accessible probability distributions are performed. To do so, we are interested in a parameterization all distributions that can be expressed as follows:
    \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
    Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately\footnote{$\netperm$ is discussed more thoroughly in \cref{sec:perm_matrix}.}.

@@

    In order to parameterize all such distributions, we elect to parameterize the states and measurements separately. Although there are numerous techniques that can used when parameterizing quantum states and measurements~\cite{Petz_2015, Hedemann_2013,Fujii_2005,James_2001,Grasmair_2014,Neilsen_Chaung_2011}, although a single technique is presented in \cref{sec:unitary_group} that was found to be most computationally suitable for our purposes. \Cref{sec:param_quantum_dist} expounds on our parameterized of the space of quantum distributions that can be realized on the quantum Triangle structure (\cref{fig:triangle_structure_quantum_model}) pursuant to \cref{eq:quantum_model_triangle_pvms}. Specifically, each bipartite quantum resource is modeled $2$-qubit, $4\times 4$ density matrix and each measurement is modeled as a $4$-element projective-value measure.

    % \subsection{Numerical Optimization Results}
    \label{sec:results}

    For each inequality $I$, we define the relative violation $V_F$ to be maximum violation relative to the violation achieved by the Fritz distribution.
    \[ V_F = \f{\min_{P}\bc{I\br{P}}}{I\br{P_F}} \]

@@

    Fritz's Problem is concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}. When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a single bipartite quantum state. In the Triangle structure, the observable nodes $A,B,C$ have access to potentially three different bipartite quantum states. As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.}. The question, as proposed by \ref{r:2}, remains: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states? Finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure. Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_scenario}) into the Triangle structure via the re-imagined version of the Triangle scenario (\cref{fig:triangle_structure_with_fritz_bell_embedded}). Furthermore, the logic of \cref{sec:fritz_distribution} shows that \textit{any} Bell structure compatibility inequality can be upgraded to a compatibility inequality for the Triangle structure, provided one restricts the domain of those inequalities to distributions possessing appropriate perfect correlations. Suppose one relaxed that restriction, then it becomes qualitatively reasonable to associate incompatibility via violations of upgraded inequalities with the same variety of incompatibility that is familiar in the Bell structure. Therefore, satisfying all such upgraded inequalities is a sufficient condition for a new type of incompatibility that is genuinely distinct from Bell structure incompatibility. In summary, it remains unclear whether or not \ref{r:2} or \ref{r:3} is a harder problem or if either is even feasible.

@@

    \clearpage
    \section{Quantum Parameterization of Triangle Structure}
    \label{sec:param_quantum_dist}
    \subsection{Unitary Group}
    \label{sec:unitary_group}
    To facilitate the parameterization of quantum states states and PVMs, a parameterization of the unitary group of dimension $d$ (denoted $\s{U}\br{d}$) by Spengler, Huber and Hiesmayr~\cite{Spengler_2010_Unitary} is introduced. Discussions of its application to states and measurements are deferred to \cref{sec:states} and \cref{sec:measurements} respectively.
